---
title: "regression3"
author: "Chris Qi"
date: "8/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###CASE STUDY 案例分析
前期准备
install.packages("tidyverse")
install.packages("modelr")
install.packages("broom")
install.packages("DAAG")
```{r}
# Packages
library(tidyverse)  # data manipulation and visualization
library(modelr)     # provides easy pipeline modeling functions
library(broom)      # helps to tidy up model outputs
library(DAAG)
```

读取数据
```{r}
setwd("~/R Teaching/demo code/regression3/")
advertising <- read.csv("advertising.csv")
advertising
```

检查一下，是否有缺失值？
```{r}
colSums(is.na(advertising))
```

描述统计，试一下？
```{r}
summary(advertising)
```

设置全局参数，一行两列，左右面板
销售额的箱图，纵坐标名称，标题
电视广告额的箱图，纵坐标名称，标题
再进一步，给箱图加上蓝色方框？
```{r}
par(mfrow=c(1,2 ))  # it divides graph area in two parts

boxplot(advertising$sales, col = "yellow",
         main= "SALES boxplot",
         ylab= "g per decaliter")

boxplot(advertising$TV, col = "orange",
         main= "TV boxplot",
         ylab= "percent values")
```

找出异常值
```{r}
# sales outliers
boxplot.stats(advertising$sales)$out 
```

sales直方图
```{r}
qplot(sales, data = advertising, geom="histogram", binwidth=1, 
      fill=I("azure4"), col=I("azure3")) +
  labs(title = "sales") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x ="sales (units)") +
  labs(y = "Frequency") +
  scale_y_continuous(breaks = c(0,2,4,6,8,10,12,14,16,18), minor_breaks = NULL) +
  scale_x_continuous(breaks = c(1,5,10,20,30,50), minor_breaks = 5) +
  geom_vline(xintercept = mean(advertising$sales), show_guide=TRUE, color
             ="red", labels="Average") +
  geom_vline(xintercept = median(advertising$sales), show_guide=TRUE, color
             ="blue", labels="Median")
```

```{r}
hist(advertising$TV)
```

依葫芦画瓢，TV 直方图？
```{r}
qplot(TV, data = advertising, geom="histogram", binwidth=5, 
      fill=I("azure4"), col=I("azure3")) +
  labs(title = "TV") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x ="AD budget in TV (in ten thousand dollars)") +
  labs(y = "Frequency") +
  scale_y_continuous(breaks = c(0,2,4,6,8,10,12,14,16,18), minor_breaks = NULL) +
  scale_x_continuous(limits = c(0, 300)) +
  geom_vline(xintercept = mean(advertising$TV), show_guide=TRUE, color
             ="red", labels="Average") +
  geom_vline(xintercept = median(advertising$TV), show_guide=TRUE, color
             ="blue", labels="Median")
```

散点图
```{r}
ggplot(advertising, aes(x=TV, y=sales))+
  geom_point(colour = "blue", size = 1.5)+
  scale_y_continuous(limits=c(0,50))+
  scale_x_continuous(limits=c(0,300))+
  theme(plot.title = element_text(hjust = 0)) +
  ggtitle("TV ad budget and sales relationship")
```
```{r}
plot(advertising$TV, advertising$sales)
```

在散点图基础上添加线性回归拟合线
```{r}
ggplot(advertising, aes(x=TV, y=sales))+
  geom_point(colour = "blue", size = 1.5)+
  scale_y_continuous(limits=c(0,50))+
  scale_x_continuous(limits=c(0,300))+
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("TV ad budget and sales relationship")+
  geom_smooth(method="lm")
```

建立模型，销售额与电视广告的线性关系
```{r}
model1 <- lm(sales ~ TV, data = advertising)
```

```{r}
summary(model1)
```

理解模型：
1. 残差 （Residuals）：
Residuals show if the predicted response values are close or not to the response values that the model predicts. 

2. 系数估计 （Estimate coefficient）

3. 系数估计的标准差（Standard error）：
Standard error measures how the coefficient estimates can vary from the actual average value of the response variable (i.e. if the model is run more times). In the current case, it’s like to say that estimated 

4. 显著度与P值 （Significance and P value）：
Test of significance of the model shows that there is strong evidence of a linear relationship between the variables. This is visually interpreted by the significance stars *** at the end of the row. This level is a threshold that is used to indicate real findings, and not the ones by chance alone.

5. R-squared 以及 adjusted R-squared
For the simple linear regression, R-squared is the square of the correlation between two variables. Its value can vary between 0 and 1: a value close to 0 means that the regression model does not explain the variance in the response variable, while a number close to 1 that the observed variance in the response variable is well explained. In the current case, R-squared suggests the linear model fit explains a 80.1% of the variance observed in the data.

回归诊断作图
1. Residuals vs Fitted values
```{r}
plot(model1, pch=16, col="blue", lty=1, lwd=2, which=1)
```
2. Normal Q-Q
```{r}
plot(model1, pch=16, col="blue", lty=1, lwd=2, which=2)
```
3. cook's distance, 单个样本对模型的“贡献”
```{r}
plot(model1, pch=16, col="blue", lty=1, lwd=2, which=4)
```

模型改进，标记异常值
```{r}
advertising$outlier = ifelse(advertising$sales>40,"Y","N") # create condition Yes/No if outlier
```

```{r}
ggplot(data=advertising, aes(x=TV, y=sales, col=as.factor(outlier)))+
  geom_point()+
  ggtitle("TV ads and sales")+
  scale_y_continuous(limits=c(0,50))+
  scale_x_continuous(limits=c(0,300))+
  theme(plot.title = element_text(hjust = 0.5))
```

剔除异常值，创建新数据
```{r}
ad_new<-subset(advertising, sales<40)
```

用新数据从新估计模型
```{r}
model2 <- lm(sales~TV,data=ad_new )
```

新旧模型，哪个好，为什么？
```{r}
summary(model2)
summary(model1)
```

换个姿势，再比较？
```{r}
AIC(model2)
AIC(model1)

BIC(model2)
BIC(model1)

```

再试一试机器学习入门？
```{r}
set.seed(100) # 设置种子点，以便重复再现同样的结果
trainingRowIndex <- sample(1:nrow(ad_new), 0.7*nrow(ad_new)) 
# 将数据七三分，training vs. testing
train <- ad_new[trainingRowIndex, ] # model training data
test <- ad_new[-trainingRowIndex, ] # test data
```

用训练数据建模，将得到的模型运用到测试数据来做预测
```{r}
modTrain <- lm(sales~TV, data=train)  # build the model
predict <- predict(modTrain, test)  # predicted values
summary(modTrain)
```

将预测数据和实际数据放在一起（针对测试数据而言），计算相关系数，来衡量模型
```{r}
act_pred <- data.frame(cbind(actuals=test$sales, predicteds=predict)) # actuals_predicteds 
cor(act_pred) # correlation_accuracy
```

实际对比一下原始数据和预测数据
```{r}
head(act_pred, n=10)
```

还可以再进一步，交叉验证：从上面7，3分的训练测试数据得到的模型表现不错，这是不是偶然碰巧的结果？
随机把数据分成K等份，K-1做训练，1做测试。得到k种结果，看看预测结果之间偏差如何？
k- Fold Cross validation
曲线是否平行
```{r}
kfold <- CVlm(data = ad_new, form.lm = formula(sales ~ TV), m=5, 
                   dots = FALSE, seed=123, legend.pos="topleft",
                   main="Cross Validation; k=5",
                   plotit=TRUE, printit=FALSE)
```