---
title: "Data Maniac 第一期第八课"
author: "Chris Qi"
date: "7/26/2018"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(hflights)
knitr::opts_chunk$set(echo = TRUE)
```

## Data Manipulation 数据操作

### for loops in R (循环)
```{r}
primes_list<-list(2,3,5,7,11,13)
for (i in 1:length(primes_list)) {
  print(primes_list[[i]])
}
```

### dplyr package
```{r hflights}
#简单查看数据
head(hflights,3)
```

### 两种方法查看每个月第一天的飞行数据
```{r}
#basic R
hflights[hflights$Month==1 & hflights$DayofMonth==1, ]
```

```{r}
#filter function from dplyr
filter(hflights, Month==1, DayofMonth==1)
```


###filter筛选AA and UA
```{r}
#前两个样本
head(filter(hflights, UniqueCarrier=="AA" | UniqueCarrier=="UA"),3)
```

```{r}
#后两个样本
tail(filter(hflights, UniqueCarrier=="AA" | UniqueCarrier=="UA"),2)
```

```{r}
#包含AA 和UA的所有样本
filter(hflights, UniqueCarrier %in% c("AA", "UA"))
```

```{r}
# base R approach to select DepTime, ArrTime, and FlightNum columns
head(hflights[, c("DepTime", "ArrTime", "FlightNum")])
```


use colon to select multiple contiguous columns, and use `contains` to match columns by name
note: `starts_with`, `ends_with`, and `matches` (for regular expressions) can also be used to match columns by name
```{r}
select(hflights, Year:DayofMonth, contains("Taxi"), contains("Delay"))
```

nesting method to select UniqueCarrier and DepDelay columns and filter for delays over 60 minutes
```{r}
head(
  filter(
    select(hflights, UniqueCarrier, DepDelay), 
    DepDelay > 60))
```

Pipes
```{r}
hflights %>%
  select(UniqueCarrier, DepDelay) %>%
  filter(DepDelay > 60) %>%
  head()
```

```{r}
hflights %>%
  select(UniqueCarrier, DepDelay)%>%
  head()
```

create two vectors and calculate Euclidian distance between them
```{r}
x1 <- 1:5; x2 <- 2:6
```

Usual 
```{r}
sqrt(sum((x1-x2)^2))
```

chaining method
```{r}
(x1-x2)^2 %>% 
  sum() %>% 
  sqrt()
```

base R approach to select UniqueCarrier and DepDelay columns and sort by DepDelay
```{r}
head(hflights[order(hflights$DepDelay), 
              c("UniqueCarrier", "DepDelay")])
```

```{r}
# dplyr approach
hflights %>%
  select(UniqueCarrier, DepDelay)%>%
  arrange(DepDelay) %>%
  head()
```

base R approach to create a new variable Speed (in mph)
```{r}
hflights$Speed <- (hflights$Distance / hflights)$AirTime*60
head(hflights[, c("Distance", "AirTime", "Speed")])
```

dplyr approach (prints the new variable but does not store it)
```{r}
hflights %>%
  select(Distance, AirTime) %>%
  mutate(Speed = Distance/AirTime*60) %>%
  head()
```

store the new variable: 
```{r}
hflights <- hflights %>% 
  mutate(Speed = Distance/AirTime*60)
```

base R approaches to calculate the average arrival delay to each destination
```{r}
head(aggregate(ArrDelay ~ Dest, hflights, mean))
```

dplyr approach: create a table grouped by Dest, and then summarise each group by taking the mean of ArrDelay
```{r}
hflights %>%
  group_by(Dest) %>%
  summarise(avg_delay = mean(ArrDelay, na.rm=TRUE)) %>%
  head()
```

for each carrier, calculate the percentage of hflights cancelled or diverted
```{r}
hflights %>%
  group_by(UniqueCarrier) %>%
  summarise_each(funs(mean), Cancelled, Diverted) %>%
  head()
```

for each carrier, calculate the minimum and maximum arrival and departure delays
```{r}
hflights %>%
  group_by(UniqueCarrier) %>%
  summarise_each(funs(min(., na.rm=TRUE), max(., na.rm=TRUE)), matches("Delay")) %>%
  head()
```

for each day of the year, count the total number of hflights and sort in descending order
```{r}
hflights %>%
  group_by(Month, DayofMonth) %>%
  summarise(flight_count = n()) %>%
  arrange(desc(flight_count)) %>%
  head()
```

rewrite more simply with the `tally` function
```{r}
hflights %>%
  group_by(Month, DayofMonth) %>%
  tally(sort = TRUE)
```

for each destination, count the total number of hflights and the number of distinct planes that flew there
```{r}
hflights %>%
  group_by(Dest) %>%
  summarise(flight_count = n(), plane_count = n_distinct(TailNum)) %>%
  head()
```

for each destination, show the number of cancelled and not cancelled hflights
```{r}
hflights %>%
  group_by(Dest) %>%
  select(Cancelled) %>%
  table() %>%
  head()
```

for each carrier, calculate which two days of the year they had their longest departure delays
note: smallest (not largest) value is ranked as 1, so you have to use `desc` to rank by largest value
```{r}
hflights %>%
  group_by(UniqueCarrier) %>%
  select(Month, DayofMonth, DepDelay) %>%
  filter(min_rank(desc(DepDelay)) <= 2) %>%
  arrange(UniqueCarrier, desc(DepDelay)) %>%
  head()
```

for each carrier, calculate which two days of the year they had their longest departure delays --- rewrite previous with the `top_n` function
```{r}
hflights %>%
  group_by(UniqueCarrier) %>%
  select(Month, DayofMonth, DepDelay) %>%
  top_n(2) %>%
  arrange(UniqueCarrier, desc(DepDelay))
```

for each month, calculate the number of hflights and the change from the previous month
```{r}
hflights %>%
  group_by(Month) %>%
  summarise(flight_count = n()) %>%
  mutate(change = flight_count - lag(flight_count))
```

rewrite previous with the `tally` function
```{r}
hflights %>%
  group_by(Month) %>%
  tally() %>%
  mutate(change = n - lag(n))
```

randomly sample a fixed number of rows, without replacement
```{r}
hflights %>% sample_n(5)
```

randomly sample a fraction of rows, with replacement
```{r}
hflights %>% sample_frac(0.25, replace=TRUE)
```

base R approach to view the structure of an object
```{r}
str(hflights)
```

dplyr approach: better formatting, and adapts to your screen width
```{r}
glimpse(hflights)
```

