---
title: "regression"
author: "Chris Qi"
date: "8/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises in class
install.packages("MASS")
install.packages("openintro")
install.packages("HistData")
install.packages("dplyr")
数据分析，从两个变量的交互关系开始-散点图
```{r}
library(MASS)
library(openintro)
library(HistData)
library(ggplot2)
library(dplyr)
```

```{r}
# Mammals scatterplot
#注释
ggplot(data = mammals, aes(x = BodyWt, y = BrainWt)) +
  geom_point()
```

```{r}
# Body dimensions scatterplot
ggplot(data = bdims, aes(x = hgt, y = wgt, color = factor(sex))) +
  geom_point()
```

```{r}
# Baseball player scatterplot
ggplot(data = mlbBat10, aes(x = OBP, y = SLG)) +
  geom_point()
```

原始数据散点图，看不出关系
```{r}
ggplot(data = mammals, aes(x = BodyWt, y = BrainWt)) +
  geom_point()
```

对数据进行对数转换，两种方式
```{r}
# Scatterplot with coord_trans()
ggplot(data = mammals, aes(x = BodyWt, y = BrainWt)) +
  geom_point() + 
  coord_trans(x = "log10", y = "log10")
```

```{r}
# Scatterplot with scale_x_log10() and scale_y_log10()
ggplot(data = mammals, aes(x = BodyWt, y = BrainWt)) +
  geom_point() +
  scale_x_log10() + scale_y_log10()
```

用散点图异常值
```{r}
# Scatterplot of SLG vs. OBP
mlbBat10 %>% 
  filter(AB >= 200) %>%
  ggplot(aes(x = OBP, y = SLG)) +
  geom_point()

# Identify the outlying player
mlbBat10 %>%
  filter(AB >= 200, OBP < 0.2)
```

用箱图检查异常值
Generally, any datapoint that lies outside the 1.5 X interquartile-range (1.5 X IQR) is considered an outlier, where, IQR is calculated as the distance between the 25th percentile and 75th percentile values for that variable.
```{r}
par(mfrow=c(1, 2))  # divide graph area in 2 columns
boxplot(cars$price, main="Price")  # box plot for 'speed'
boxplot(cars$mpgCity, main="mpg in city ")  # box plot for 'distance'
```


###计算相关系数
```{r}
ncbirths %>%
  summarize(N = n(), r = cor(weight, mage))
```

```{r}
# Compute correlation for all non-missing pairs
ncbirths %>%
  summarize(N = n(), r = cor(weight, weeks, use = "pairwise.complete.obs"))
```

```{r}
# Correlation for all baseball players
mlbBat10 %>%
  summarize(N = n(), r = cor(OBP, SLG))
```

```{r}
# Correlation for all players with at least 200 ABs
mlbBat10 %>%
  filter(AB >= 200) %>%
  summarize(N = n(), r = cor(OBP, SLG))
```

```{r}
# Correlation of body dimensions
bdims %>%
  group_by(sex) %>%
  summarize(N = n(), r = cor(hgt, wgt))
```

```{r}
# Correlation among mammals, with and without log
mammals %>%
  summarize(N = n(), 
            r = cor(BodyWt, BrainWt), 
            r_log = cor(log(BodyWt), log(BrainWt)))
```

线性回归
```{r}
# Scatterplot with regression line
ggplot(data = bdims, aes(x = hgt, y = wgt)) + 
  geom_point()
```

```{r}
# Scatterplot with regression line
ggplot(data = bdims, aes(x = hgt, y = wgt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```
























