---
title: "Data Manipulation Homework answer key"
author: "Chris Qi"
date: "8/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Maniac 第一期
安装这两个包，运行下面的代码：
install.packages("dplyr")
install.packages("hflights")

载入这两个包，运行下的的代码：
```{r loadPackage, echo=FALSE}
library(dplyr)
library(hflights)
```

Call both head() and summary() on hflights
```{r}
head(hflights)
summary(hflights)
```

A data scientist must be familiar with his or 
her data. Experiment with the data set in the 
console and maybe try to generate some insightful 
plots.

How many observations and how many variables 
are contained in the hflights data set?
```{r}
dim(hflights)
```

Convert the hflights data.frame into a hflights tbl
```{r}
hflights<-tbl_df(hflights)

# Display the hflights tbl
hflights
```

Create the object carriers
```{r}
carriers <- hflights$UniqueCarrier
```

Change labels
```{r}
lut <- c("AA" = "American", "AS" = "Alaska", "B6" = "JetBlue", "CO" = "Continental", 
         "DL" = "Delta", "OO" = "SkyWest", "UA" = "United", "US" = "US_Airways", 
         "WN" = "Southwest", "EV" = "Atlantic_Southeast", "F9" = "Frontier", 
         "FL" = "AirTran", "MQ" = "American_Eagle", "XE" = "ExpressJet", "YV" = "Mesa")
```

Add the Carrier column to hflights
```{r}
hflights$Carrier <- lut[hflights$UniqueCarrier]
```

Glimpse at hflights
```{r}
glimpse(hflights)
```

The lookup table
```{r}
lut <- c("A" = "carrier", "B" = "weather", "C" = "FFA", "D" = "security", "E" = "not cancelled")
```

Add the Code column
```{r}
hflights$Code <-lut[hflights$CancellationCode]
```

Glimpse at hflights
```{r}
glimpse(hflights)
```

Print out a tbl with the four columns of hflights related to delay
```{r}
select(hflights, ActualElapsedTime)
```

Print out the columns Origin up to Cancelled of hflights
...{r}
dplyr::select(hflights, Origin:Cancelled)
...

Find the most concise way to select: columns Year up to and including DayOfWeek, columns ArrDelay up to and including Diverted. You can examine the order of the variables in hflights with names(hflights) in the console.
```{r}
select(hflights, - (DepTime:AirTime))
```

### Helper functions for variable selection
dplyr comes with a set of helper functions that can help you select groups of variables inside a select() call:

starts_with("X"): every name that starts with "X",
ends_with("X"): every name that ends with "X",
contains("X"): every name that contains "X",
matches("X"): every name that matches "X", where "X" can be a regular expression,
num_range("x", 1:5): the variables named x01, x02, x03, x04 and x05,
one_of(x): every name that appears in x, which should be a character vector.
**Pay attention here: When you refer to columns directly inside select(), you don't use quotes. If you use the helper functions, you do use quotes.

Use select() and a helper function to print out a tbl that contains just ArrDelay and DepDelay of hflights.
```{r}
select(hflights, ends_with("Delay"))
```

Use a combination of helper functions and variable names to print out only the UniqueCarrier, FlightNum, TailNum, Cancelled, and CancellationCode columns of hflights.
```{r}
select(hflights, UniqueCarrier, ends_with("Num"), starts_with("Cancel"))
```

Find the most concise way to return the following columns with select and its helper functions: DepTime, ArrTime, ActualElapsedTime, AirTime, ArrDelay, DepDelay. Use only helper functions!
```{r}
select(hflights, contains("Tim"), contains("Del"))
```

Comparison to base R
To see the added value of the dplyr package, it is useful to compare its syntax with base R. Up to now, you have only considered functionality that is also available without the use of dplyr. The elegance and ease-of-use of dplyr is a great plus though.

Finish select call so that ex1d matches ex1r
```{r}
ex1r <- hflights[c("TaxiIn", "TaxiOut", "Distance")]
ex1d <- select(hflights,contains("Taxi"), Distance)
```

Finish select call so that ex2d matches ex2r
```{r}
ex2r <- hflights[c("Year", "Month", "DayOfWeek", "DepTime", "ArrTime")]
ex2d <- select(hflights,Year,Month,(DayOfWeek:ArrTime))
```

Finish select call so that ex3d matches ex3r
```{r}
ex3r <- hflights[c("TailNum", "TaxiIn", "TaxiOut")]
ex3d <- select(hflights,contains("Taxi"),TailNum)
```
##Mutating is creating
mutate() is the second of five data manipulation functions you will get familiar with in this course. mutate() creates new columns which are added to a copy of the dataset.

Take this example that adds a new column, z, which is the element-wise sum of the columns x and y, to the data frame df:  
mutate(df, z = x + y)

Create a new data frame, g1, which is the data frame hflights with an additional column: ActualGroundTime, the difference between ActualElapsedTime and AirTime.
```{r}
g1<-mutate(hflights,ActualGroundTime =ActualElapsedTime- AirTime)
```

Extend g1 further, by adding an additional column GroundTime. This column is the sum of the TaxiIn and TaxiOut columns. Store the resulting data frame in g2. Check in the console that the GroundTime and ActualGroundTime columns are equal.
```{r}
g2<-mutate(g1,GroundTime=TaxiIn+TaxiOut)
```

Add a new variable to g2 named AverageSpeed that denotes the average speed that each plane flew in miles per hour. Save the resulting dataset as g3. Use the following formula: Distance / AirTime * 60.
```{r}
g3<-mutate(g2, AverageSpeed=Distance / AirTime * 60)
```

Print out g3.
```{r}
g3
```

###Add multiple variables using mutate
So far you've added variables to hflights one at a time, but you can also use mutate() to add multiple variables at once. To create more than one variable, place a comma between each variable that you define inside mutate().

mutate() even allows you to use a new variable while creating a next variable in the same call. In this example, the new variable x is directly reused to create the new variable y:

mutate(my_df, x = a + b, y = x + c)

Adapt the code that builds m1: add a variable loss_ratio, which is the ratio of loss to DepDelay.
```{r}
m1 <- mutate(hflights, loss = ArrDelay - DepDelay)
m1 <- mutate(m1,loss_ratio=loss/DepDelay)
```

Create a tbl m2 from hflights by adding three variables:
TotalTaxi, which is the sum of TaxiIn and TaxiOut;
ActualGroundTime, which is the difference of ActualElapsedTime and AirTime;
Diff, the difference between the two newly created variables. This column should be zero for all observations!
```{r}
m2<-mutate(hflights,TotalTaxi=TaxiIn+TaxiOut,ActualGroundTime=ActualElapsedTime-AirTime, Diff=TotalTaxi- ActualGroundTime)
```

###Logical operators
R comes with a set of logical operators that you can use inside filter():

x < y, TRUE if x is less than y
x <= y, TRUE if x is less than or equal to y
x == y, TRUE if x equals y
x != y, TRUE if x does not equal y
x >= y, TRUE if x is greater than or equal to y
x > y, TRUE if x is greater than y
x %in% c(a, b, c), TRUE if x is in the vector c(a, b, c)
The following example filters df such that only the observations for which a is positive, are kept:

filter(df, a > 0)


Print out all flights in hflights that traveled 3000 or more miles.
```{r}
filter(hflights,Distance>=3000)
```

Print out all flights in hflights flown by JetBlue, Southwest, or Delta.
```{r}
filter(hflights,UniqueCarrier %in%c("JetBlue","Southwest","Delta"))
```

Extract from hflights all flights where taxiing took longer than the actual flight. Avoid the use of mutate() and do the math directly in the logical expression of filter().
```{r}
filter(hflights, TaxiOut+TaxiIn>AirTime)
```

##Combining tests using boolean operators
R also comes with a set of boolean operators that you can use to combine multiple logical tests into a single test. These include & (and), | (or), and ! (not). Instead of using the & operator, you can also pass several logical tests to filter(), separated by commas. The following two calls are completely equivalent:

filter(df, a > 0 & b > 0)
filter(df, a > 0, b > 0)
Next, is.na() will also come in handy. This example keeps the observations in df for which the variable x is not NA:

filter(df, !is.na(x))

Use R's logical and boolean operators to select just the rows where a flight left before 5:00 am (500) or arrived after 10:00 pm (2200).
```{r}
filter(hflights,ArrTime>2200|DepTime<500)
```

Print out all of the flights that departed late but arrived ahead of schedule. Use DepDelay and ArrDelay for this.
```{r}
filter(hflights, DepDelay > 0, ArrDelay < 0)
```

Find all of the flights that were cancelled after being delayed. These are flights that were cancelled, while having a DepDelay greater than zero.
```{r}
filter(hflights, Cancelled == 1, DepDelay > 0)
```

### Blend together what you've learned!
So far, you have learned three data manipulation functions in the dplyr package. Time for a summarizing exercise. You will generate a new dataset from the hflights dataset that contains some useful information on flights that had JFK airport as their destination. You will need select(), mutate() and filter().

First, use filter() to select the flights that had JFK as their destination and save this result to c1.
```{R}
c1<-filter(hflights, Dest%in%c("JFK"))
```

Second, add a new column named Date to c1: paste() together the Year, Month and DayofMonth variables, separate them by a "-" by using the sep attribute of paste(). Save the resulting data frame as c2.
```{r}
c2<-mutate(c1, Date=paste(Year,Month,DayofMonth,sep="_"))
```

Finally, select some columns to provide an overview: Date, DepTime, ArrTime and TailNum, in this order. Do not assign the resulting data frame to a variable; just print it to the console.
```{r}
select(c2, Date,DepTime, ArrTime, TailNum)
```


###Recap on select, mutate and filter
With select(), mutate() and filter(), you can already reveal interesting information from a dataset. Through a combination of these expressions or by the use of a one-liner, try to answer the following question:

How many weekend flights flew a distance of more than 1000 miles but had a total taxiing time below 15 minutes?
```{r}
filter(hflights, DayOfWeek %in% c(6,7), Distance > 1000, TaxiIn + TaxiOut < 15)
```

###Arranging your data
arrange() can be used to rearrange rows according to any type of data. If you pass arrange() a character variable, for example, R will rearrange the rows in alphabetical order according to values of the variable. If you pass a factor variable, R will rearrange the rows according to the order of the levels in your factor (running levels() on the variable reveals this order).

dtc has already been defined.
```{r}
dtc <- filter(hflights, Cancelled == 1, !is.na(DepDelay))
```

It's up to you to write some arrange() expressions to display its contents appropriately!

Arrange dtc, by departure delays so that the shortest departure delay is at the top of the data set.
```{r}
arrange(dtc,DepDelay)

```

Arrange dtc so that flights that were cancelled for the same reason appear next to each other.
```{r}
arrange(dtc, CancellationCode)
```

Arrange dtc so that flights by the same carrier appear next to each other. Within each carrier, flights that have smaller departure delays appear before flights that have higher departure delays. Do this in a one-liner.
```{r}
arrange(dtc,UniqueCarrier,DepDelay)
```


###Reverse the order of arranging
By default, arrange() arranges the rows from smallest to largest. Rows with the smallest value of the variable will appear at the top of the data set. You can reverse this behavior with the desc() function. arrange() will reorder the rows from largest to smallest values of a variable if you wrap the variable name in desc() before passing it to arrange().

Arrange hflights so that flights by the same carrier appear next to each other and within each carrier, flights that have larger departure delays appear before flights that have smaller departure delays.

```{r}
arrange(hflights,UniqueCarrier,DepDelay)

```

Arrange the flights in hflights by their total delay (the sum of DepDelay and ArrDelay). Try to do this directly inside arrange().
```{r}
arrange(hflights,desc(DepDelay + ArrDelay))
```

###The syntax of summarise
summarise(), the last of the 5 verbs, follows the same syntax as mutate(), but the resulting dataset consists of a single row instead of an entire new column in the case of mutate().

In contrast to the four other data manipulation functions, summarise() does not return an altered copy of the dataset it is summarizing; instead, it builds a new dataset that contains only the summarising statistics.

Use summarise() to print out a summary of hflights containing two variables: min_dist, the shortest distance flown, and max_dist, the longest distance flown.
```{r}
summarise(hflights, min_dist=min(Distance),max_dist=max(Distance))
```

Print out a summary of hflights with a single variable, max_div: the longest Distance for diverted flights. You will need one of the four other verbs to do this!
```{r}
summarise(filter(hflights,Diverted==1), max_div=max(Distance))
```

Aggregate functions
You can use any function you like in summarise() so long as the function can take a vector of data and return a single number. R contains many aggregating functions, as dplyr calls them:

min(x) - minimum value of vector x.
max(x) - maximum value of vector x.
mean(x) - mean value of vector x.
median(x) - median value of vector x.
quantile(x, p) - pth quantile of vector x.
sd(x) - standard deviation of vector x.
var(x) - variance of vector x.
IQR(x) - Inter Quartile Range (IQR) of vector x.
diff(range(x)) - total range of vector x.

Remove rows that have NAs in the arrival delay column and save the resulting dataset to temp1.
```{r}
temp1<-filter(hflights,!is.na(ArrDelay))
```

Print out a summary of temp1 with the following variables (in this order):
earliest: the minimum arrival delay,
average: the average arrival delay,
latest: the longest arrival delay,
sd: the standard deviation for arrival delays.
```{r}
summarise(temp1,earliest=min(ArrDelay),average=mean(ArrDelay),latest=max(ArrDelay),sd=sd(ArrDelay))
```

Filter hflights such that only rows that have no NA TaxiIn and no NA TaxiOut are kept; save this temporary result to temp2.
```{r}
temp2<-filter(hflights,!is.na(TaxiIn),!is.na(TaxiOut))
```

Print out a summary of temp2, with one variable, max_taxi_diff: the biggest absolute difference in time between TaxiIn and TaxiOut for a single flight.
```{r}
summarise(temp2, max_taxi_diff=max(TaxiOut-TaxiIn))
```

###dplyr aggregate functions
dplyr provides several helpful aggregate functions of its own, in addition to the ones that are already defined in R. These include:

first(x) - The first element of vector x.
last(x) - The last element of vector x.
nth(x, n) - The nth element of vector x.
n() - The number of rows in the data.frame or group of observations that summarise() describes.
n_distinct(x) - The number of unique values in vector x.
Next to these dplyr-specific functions, you can also turn a logical test into an aggregating function with sum() or mean(). A logical test returns a vector of TRUE's and FALSE's. When you apply sum() or mean() to such a vector, R coerces each TRUE to a 1 and each FALSE to a 0. sum() then represents the total number of observations that passed the test; mean() represents the proportion.

Print out a summary of hflights with the following variables:
n_obs: the total number of observations,
n_carrier: the total number of carriers,
n_dest: the total number of destinations,
aa, a tbl with all flights flown by American Airlines, is already available.
```{r}
summarise(hflights,
          n_obs=n(),
          n_carrier=n_distinct(UniqueCarrier),
          n_dest=n_distinct(Dest))
```

```{r}
aa <- filter(hflights, UniqueCarrier == "AA")
```
Print out a summary of aa with the following variables:
n_flights: the total number of flights (each observation is a flight),
n_canc: the total number of cancelled flights,
avg_delay: the average arrival delay of flights whose delay is not NA (na.rm = TRUE).
```{r}
summarise(aa,
          n_flights=n(), 
          n_canc=sum(Cancelled==1),
          avg_delay=mean(!is.na(ArrDelay)),
          avg_delay_2=mean(ArrDelay, na.rm=TRUE)
                         )
```

```{r}
v<-c(2,3,4,NA)
v
class(v)
mean(v)
mean(!is.na(v))
mean(v, na.rm=TRUE)
```


###Overview of syntax: Pipe
As another example of the %>%, have a look at the following two commands that are completely equivalent:

mean(c(1, 2, 3, NA), na.rm = TRUE)
c(1, 2, 3, NA) %>% mean(na.rm = TRUE)
The %>% operator allows you to extract the first argument of a function from the arguments list and put it in front of it, thus solving the Dagwood sandwich problem.

Use dplyr functions and the pipe operator to transform the following English sentences into R code:

Take the hflights data set and then ...
Add a variable named diff that is the result of subtracting TaxiIn from TaxiOut, and then ...
Pick all of the rows whose diff value does not equal NA, and then ...
Summarise the data set with a value named avg that is the mean diff value.
```{r}
piped<-hflights%>%
              mutate(diff=TaxiOut-TaxiIn)%>%
              filter(!is.na(diff))%>%
              summarise(avg=mean(diff))
```          

Drive or fly? Part 1 of 2
You can answer sophisticated questions by combining the verbs of dplyr. Over the next few exercises you will examine whether it sometimes makes sense to drive instead of fly. You will begin by making a data set that contains relevant variables. Then, you will find flights whose equivalent average velocity is lower than the velocity when traveling by car.

In the following instructions, you have to carry out a series of dplyr verbs on the hflights dataset. Make sure to use the %>% operator to chain them all together.

mutate() the hflights dataset and add two variables:
RealTime: the actual elapsed time plus 100 minutes (for the overhead that flying involves) and
mph: calculated as Distance / RealTime * 60, then
filter() to keep observations that have an mph that is not NA and that is below 70, finally
summarise() the result by creating four summary variables:
n_less, the number of observations,
n_dest, the number of destinations,
min_dist, the minimum distance and
max_dist, the maximum distance.

```{r}
hflights%>%
  mutate(RealTime=ActualElapsedTime+100,
         mph=(Distance/RealTime) * 60)%>%
  filter(!is.na(mph), mph<70)%>%
  summarise(n_less=n(),
            n_dest=n_distinct(Dest),
            min_dist=min(Distance),
            max_dist=max(Distance))
```


Drive or fly? Part 2 of 2
The previous exercise suggested that some flights might be less efficient than driving in terms of speed. But is speed all that matters? Flying imposes burdens on a traveler that driving does not. For example, airplane tickets are very expensive. Air travelers also need to limit what they bring on their trip and arrange for a pick up or a drop off. Given these burdens we might demand that a flight provide a large speed advantage over driving.

Let's define preferable flights as flights that are at least 50% faster than driving, i.e. that travel 105 mph or greater in real time. Also, assume that cancelled or diverted flights are less preferable than driving.

The mutate() call from the previous exercise is already coded up; can you add more pipes and verbs to the command?

filter() the result of mutate to:
keep observations that have an mph under 105 or for which Cancelled equals 1 or for which Diverted equals 1.
summarise() the result by creating four summary variables:
n_non, the number of observations,
n_dest, the number of destinations,
min_dist, the minimum distance and
max_dist, the maximum distance.

```{r}
hflights%>%
  mutate(RealTime=ActualElapsedTime+100,
         mph=(Distance/RealTime) * 60)%>%
  filter(mph<105|Cancelled==1|Diverted==1)%>%
  summarise(n_non=n(),
            n_dest=n_distinct(Dest),
            min_dist=min(Distance),
            max_dist=max(Distance))
```

Advanced piping exercise
Let's use hflights to answer another question: How many flights were overnight flights?

filter() the hflights tbl to keep only observations whose DepTime is not NA, whose ArrTime is not NA and for which DepTime exceeds ArrTime.
Pipe the result into a summarise() call to create a single summary variable: num, that simply counts the number of observations.
```{r}
hflights%>%
  filter(!is.na(DepTime),!is.na(ArrTime),DepTime>ArrTime)%>%
  summarise(num=n())
```

Unite and conquer using group_by
As Garrett explained, group_by() lets you define groups within your data set. Its influence becomes clear when calling summarise() on a grouped dataset: summarising statistics are calculated for the different groups separately.

In this exercise, you are going to create an ordered per-carrier summary of hflights by combining group_by(), summarise() and arrange().

Use group_by() to group hflights by UniqueCarrier.
summarise() the grouped tbl with two summary variables:
p_canc, the percentage of cancelled flights
avg_delay, the average arrival delay of flights whose delay does not equal NA.
Finally, order the carriers in the summary from low to high by their average arrival delay. Use percentage of flights cancelled to break any ties.

```{r}
hflights %>%
   group_by(UniqueCarrier) %>%
   summarise(p_canc = mean(Cancelled == 1) * 100, 
             avg_delay = mean(ArrDelay, na.rm = TRUE)) %>%
   arrange(avg_delay, p_canc)
```

Combine group_by with mutate
You can also combine group_by() with mutate(). When you mutate grouped data, mutate() will calculate the new variables independently for each group. This is particularly useful when mutate() uses the rank() function, that calculates within-group rankings. rank() takes a group of values and calculates the rank of each value within the group, e.g.

rank(c(21, 22, 24, 23))
has output

[1] 1 2 4 3
As with arrange(), rank() ranks values from the smallest to the largest.


filter() the hflights tbl to only keep observations for which ArrDelay is not NA and positive.
Use group_by() on the result to group by UniqueCarrier.
Next, use summarise() to calculate the average ArrDelay per carrier. Call this summary variable avg.
Feed the result into a mutate() call: create a new variable, rank, calculated as rank(avg).
Finally, arrange by this new rank variable

```{r}
hflights%>%
  filter(!is.na(ArrDelay),ArrDelay>0)%>%
  group_by(UniqueCarrier)%>%
  summarise(avg=mean(ArrDelay))%>%
  mutate(rank=rank(avg))%>%
  arrange(rank)
```


###Advanced group_by exercises
By now you've learned the fundamentals of dplyr: the five data manipulation verbs and the additional group_by() function to discover interesting group-wise statistics. The next challenges are an all-encompassing review of the concepts you have learned about. We already provided you with a template of the piped call that can solve the exercises. Up to you to finish all dplyr calls! For simplicity, you can include cancelled flights in your answers, so you shouldn't filter based on the Cancelled column.


How many airplanes flew to only one destination? The tbl you print out should have a single column, named nplanes and a single row.

```{r}
hflights%>%
  group_by(TailNum)%>%
  summarise(ndest=n_distinct(Dest))%>%
  filter(ndest==1)%>%
  summarise(nplanes=n())
```

Find the most visited destination for each carrier. The tbl you print out should contain four columns:
UniqueCarrier and Dest,
n, how often a carrier visited a particular destination,
rank, how each destination ranks per carrier. rank should be 1 for every row, as you want to find the most visited destination for each carrier.
```{r}
hflights %>% 
  group_by(UniqueCarrier, Dest) %>%
  summarise(n = n()) %>%
  mutate(rank = rank(desc(n))) %>%
  filter(rank == 1)
```

###dplyr deals with different types
hflights2 is a copy of hflights that is saved as a data table. hflights2 was made available in the background using the following code:
```{r}
library(data.table)
hflights2 <- as.data.table(hflights)
```

hflights2 contains all of the same information as hflights, but the information is stored in a different data structure. You can see this structure by typing hflights2 at the command line.

Even though hflights2 is a different data structure, you can use the same dplyr functions to manipulate hflights2 as you used to manipulate hflights.

Use summarise() to calculate n_carrier, the total number of unique carriers in hflights2. Whether or not you use the pipe is up to you!

```{r}
hflights2%>%
summarise(n_carrier=n_distinct(UniqueCarrier))
```


dplyr and mySQL databases
DataCamp hosts a mySQL database with data about flights that departed from New York City in 2013. The data is similar to the data in hflights, but it does not contain information about cancellations or diversions. With the tbl() function, we already created a reference to a table in this information.

Although nycflights is a reference to data that lives outside of R, you can use the dplyr commands on them as usual. Behind the scenes, dplyr will convert the commands to the database's native language (in this case, SQL), and return the results. This allows you to pull data that is too large to fit in R: only the fraction of the data that you need will actually be downloaded into R, which will usually fit into R without memory issues.


Try to understand the code that creates nycflights, a reference to a MySQL table.
Set up a connection to the mysql database:
```{r}
my_db <- src_mysql(dbname = "dplyr", 
                   host = "courses.csrrinzqubik.us-east-1.rds.amazonaws.com", 
                   port = 3306, 
                   user = "student",
                   password = "datacamp")
```     
Reference a table within that source: nycflights
```{r}
nycflights <- tbl(my_db, "dplyr")
```

Use glimpse() to check out nycflights. Although nycflights is a reference to a tbl in a remote database, there is no difference in syntax. Look carefully: the variable names in nycflights differ from the ones in hflights!
```{r}
glimpse(nycflights)
```

Group nycflights data by carrier, then summarise() with two variables: n_flights, the number of flights flown by each carrier and avg_delay, the average arrival delay of flights flown by each carrier. Finally, arrange the carriers by average delay from low to high.

```{r}
nycflights%>%
  group_by(carrier)%>%
  summarise(n_flights=n(), avg_delay=mean(arr_delay))%>%
  arrange(avg_delay)
```





