---
title: "Data Visualization 1 Exercise"
author: "Chris Qi"
date: "8/5/2018"
output: html_document
---

#基础练习第二波：

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tutorial::go_interactive()
```


Apply the plot() function to the whiteside data frame.

探索性绘图，方便自己理解变量之间的大概关系
使用plot()，得到数据里面每两个变量之间的散点图

```{r ex="ex1", type="pre-exercise-code"}
# Load MASS package
library(dplyr)
library(MASS)
library(robustbase)
library(insuranceData)
library(car)
```

```{r ex="ex1", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
plot(whiteside)
```


使用 plot() 函数和数据“whiteside”， 绘制散点图来展示Temp与Gas之间的关系，并使用xlab, ylab添加坐标标示 "Outside temperature" and "Heating gas consumption"。

```{r ex="ex2", type="sample-code"}
plot(whiteside$,whiteside$,
)
```

```{r ex="ex2", type="solution"}
plot(whiteside$Temp,whiteside$Gas,
     xlab="Outside temperature",
     ylab= "Heating gas consumption")
```

Adding details to a plot using point shapes, color, and reference lines
为绘图添加细节，例如数据点的形状，颜色以及参照线。
使用数据“Cars93”来练习：

Price: the average sale price for a car

Max.Price: the highest recorded price for that car

Min.Price: the lowest recorded price for that car

Use the abline() function to add a dashed equality reference line (i.e., a line with y-intercept 0 and slope 1). See abline() to learn what arguments a and b refer to.

使用 'glimpse()' 查看数据'Cars93'：

```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex3", type="solution"}
glimpse(Cars93)
```


探索最高价和价格之间的关系：

Use the plot() function to create a scatterplot of the Max.Price variable versus the Price variable, specifying the pch and col parameters so the data points are represented as red solid triangles. The pch value to plot solid triangles is 17.
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
plot(Cars93$Max.Price, Cars93$Price,col="red",pch=17)
```

添加最低价与价格的散点图：
Use the points() function to add a second set of points to your scatterplot, representing Min.Price versus Price, where the new data points are represented as blue solid circles. The pch value for solid circles is 16.

```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
plot(Cars93$Max.Price, Cars93$Price,col="red",pch=17)
points(Cars93$Min.Price,Cars93$Price,col="blue",pch=16)
```

添加一条0为截距，1为斜率的参照线
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
plot(Cars93$Max.Price, Cars93$Price,col="red",pch=17)
points(Cars93$Min.Price,Cars93$Price,col="blue",pch=16)
abline(a = 0, b = 1, lty = 2)
```


使用数据Animals2来练习全局设置面板par()，照例先查看一下
```{r}
glimpse(Animals2)
```

```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
par(mfrow = c(1,2))

# First plot: brain vs. body in its original form

plot(Animals2$brain, Animals2$body)
# Add the first title
title("Original representation")

plot(log(Animals2$brain), log(Animals2$body))
# Add the first title
title("Log-log plot")
```

柱状图经常使用。
来，我们认识一下这两个 hist()，truehist() 函数。
一个自带，一个来自 MASS package。
运行下面的函数，看看它们有什么相同和不同之处？

```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
# Set up a side-by-side plot array
par(mfrow=c(1,2))

# Create a histogram of counts with hist()
hist(Cars93$Horsepower,main="hist() plot")

# Create a normalized histogram with truehist()
truehist(Cars93$Horsepower,main="hist() plot")
```


两个变量的散点图中，如果某对或者多对数值多次重复出现，散点图无法显示数据的这一特点。
花瓣图让你看到更大的世界...
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
# Set up a side-by-side plot array
par(mfrow=c(1,2))

# Create the standard scatterplot
plot(rad~zn,data=Boston)

# Add the title
title("Standard scatterplot")

# Create the sunflowerplot
sunflowerplot(rad~zn,data=Boston)

# Add the title
title("Sunflower plot")
```

探索一下箱图的其他特点
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
#普通箱图
par(mfrow=c(1,2))
# Create a variable-width boxplot with log y-axis & horizontal labels
boxplot(crim~rad, data=Boston)
# Add a title
title("Crime rate vs. radial highway index")

#将y值取对数
boxplot(crim~rad, data=Boston, log="y")
```


使用 corrplot() function绘制相关矩阵图形
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
# Load the corrplot library for the corrplot() function
library(corrplot)

# Extract the numerical variables from UScereal
numericalVars <- UScereal[, 2:10]

# Compute the correlation matrix for these variables
corrMat <- cor(numericalVars)

# Generate the correlation ellipse plot
corrplot(corrMat, method = "ellipse")

```

最后，我们练习 plot() 函数里, type这个参数的取值，不同的type代表不同的形状：

"p" for "points"
"l" for "lines"
"o" for "overlaid" (i.e., lines overlaid with points)
"s" for "steps"
```{r ex="ex3", type="sample-code"}
#
```

```{r ex="ex1", type="solution"}
# Set up a 2-by-2 plot array
par(mfrow = c(2, 2))

# Plot the Animals2 brain weight data as points
plot(Animals2$brain, type = "p")

# Add the title
title("points")

# Plot the brain weights with lines
plot(Animals2$brain, type = "l")

# Add the title
title("lines")

# Plot the brain weights with overlaid
plot(Animals2$brain, type = "o")

# Add the title
title("overlaid")

# Plot the brain weights with lines
plot(Animals2$brain, type = "s")

# Add the title
title("steps")
```

